---
title: "Resiliency Project"
format: html
editor: visual
---

# EDA

## 
Datacodebook notes 
Potential key outcome variables: 

  - welldiet_score, 
  - flag_gooddiet (1 for welldiet_score > 60, 0 otherwise), 
  - flag_any_outcome (1 if any present of: htn, diab, obesity, hld, cancer), 
  - n_outcomes (count of these health-related outcomes). 

Everything else should hopefully be self-explanatory from the REDCap codebook, also attached.

```{r}
library(haven)
library(tidyverse)
herstory <- read_sav("../RE_ Descriptive stats - HERSTORY/herstory.sav")
```

## Welldiet
```{r}
summary(herstory$welldiet_score)
```

```{r}
ggplot(aes(x = welldiet_score, y=..density..), data = herstory) + geom_histogram() + geom_density(color = "red", lwd = 1.5)

ggplot(aes(x = welldiet_score), data = herstory) + geom_boxplot() 
```

## Flag good diet
```{r}
table(herstory$flag_gooddiet)
```
```{r}
ggplot(aes(x = flag_gooddiet), data = herstory) + geom_bar()
```
## Flag anyoutcome

```{r}
table(herstory$flag_any_outcome)
```

```{r}
ggplot(aes(x = flag_any_outcome), data = herstory) + geom_bar()
```

## n_outcomes
```{r}
table(herstory$n_outcomes)
```
```{r}
ggplot(aes(x = n_outcomes), data = herstory) + geom_bar()
```

## BRS
```{r}
table(herstory$brs_level)
summary(herstory$brs)
summary(herstory$brs)
```

## Research Questions

  1)	Is perceived stress associated with Well Diet Score (Greg question: How is perceived stress defined?  What variable is it?  I don't have a good answer to this. )
  2)	Does level of resilience (high vs low) moderate the relationship between perceived stress and diet quality (as measured by the WELL Diet Score). (Greg Question: How is resilience defined? I think this is BRS.) 
  3)	Does level of resilience (high vs low) moderate the relationship between perceived stress and diet related outcomes (aggregated measure outlined above)  

Greg Question: Is BRS something resiliency score?  
<!-- https://edinstruments.org/instruments/brief-resilience-scale-brs -->
"The brief resilience scale (BRS) was created to assess the ability to bounce back or recover from stress. The BRS is comprised of 6 items. Items 1, 3, and 5 are positively worded while items 2, 4, and 6 are negatively worded. The BRS is scored by reverse coding items 2, 4, and 6, and finding the mean of the 6 items. The Likert Scale for the BRS is as follows: 1=strongly disagree, 2=disagree, 3=neutral, 4=agree, 5=strongly agree. "

BRCS: https://www.hsph.harvard.edu/health-happiness/brief-resilient-coping-scale-brcs/

```{r}
#Resilience and food.
#BRS and food 

herstory %>% filter(!is.na(brs_level)) %>% ggplot(aes(x = as.factor(brs_level), y = welldiet_score)) + geom_boxplot() + labs(x = "BRS level", y = "Well Diet Score")
```

```{r}
#ANOVA
a <- lm(welldiet_score ~ as.factor(brs_level), data = herstory)



```
