---
title: "EDA Geography"
format: pdf
editor: visual
---

## Creating Region Variable

```{r}
#| message: false
library(haven)
library(tidyverse)
qualtrics <- read_sav("../bwnjoy_20220217_qualtrics.sav")
qualtrics <- qualtrics %>% mutate(flag_gooddiet = well_score > 60)
```

## Summary of well score and bmi
```{r}
#Well Score
summary(qualtrics$well_score)
#Depress
table(qualtrics$flag_depress)
#Good Diet Flag
table(qualtrics$flag_gooddiet + 0)
#Hypertension flag
table(qualtrics$flag_htn)
#Cancer flag
table(qualtrics$flag_cancer)
table(qualtrics$flag_hld)
#BMI
summary(qualtrics$bmi)
#Obesity
table(qualtrics$bmi > 30)
```

## Histgram of well score and bmi
```{r}
ggplot(aes(x = well_score), data = qualtrics) + geom_histogram() + theme_bw()
```

Note: Are these on the right tail possible or data errors?  80 seems like a data error.  

```{r}
ggplot(aes(x = bmi), data = qualtrics) + geom_histogram() + theme_bw()
```

## Adding region variable. 

Regions are defined based on the Census defintion found here: https://www2.census.gov/geo/pdfs/maps-data/maps/reference/us_regdiv.pdf

```{r}
qualtrics <- qualtrics %>% mutate(Region = case_when(State %in% c("Washington","Oregon","California","Montana",
                                                                  "Idaho","Nevada","Arizona","Utah","Wyoming",
                                                                  "Colorado","New Mexico") ~ "West",
                                                     State %in% c("North Dakota", "South Dakota","Nebraska","Kansas",
                                                                  "Minnesota","Iowa","Missouri","Wisconsin","Illinois",
                                                                  "Indiana","Michigan","Ohio") ~ "Midwest",
                                                     State %in% c("Texas","Oklahoma","Arkansas","Louisiana",
                                                                  "Kentucky","Tennessee","Mississippi","Alabama",
                                                                  "Florida","Georgia","South Carolina","North Carolina",
                                                                  "Virginia", "West Virginia","Maryland","Delware","District of Columbia") ~ "South",
                                                     State %in% c("Maine","Massachusetts","Connecticut","Vermont","New Hampshire",
                                                                  "New York","Pennsylvania","New Jersey") ~ "Northeast"
  
))

qualtrics$Region <- as.factor(qualtrics$Region)
```

## State and region breakdown
## Which states and regions are represented in the data?

213 of the total 512 observations (41.60%) of the observations are from Illinois.  Florida, New York, and Georgia have 43, 30, and 25 observations, respectively.  Every other state have less than 20 observtions.  

```{r}
sort(table(qualtrics$State),decreasing = TRUE)
```

## Map of where observations are from

```{r}
library(usmap)
sub <- qualtrics %>% group_by(state = State) %>% summarize(n = n())
plot_usmap(data = sub, values = "n") + scale_fill_continuous(low = "white", high = "blue", name = "Number of Observations", label = scales::comma)  
```

## Map of where observations are from (excluding Illinois)

```{r}
library(usmap)
sub <- qualtrics %>% group_by(state = State) %>% summarize(n = n()) %>% filter(state != "Illinois")
plot_usmap(data = sub, values = "n") + scale_fill_continuous(low = "white", high = "blue", name = "Number of Observations", label = scales::comma)  
```

#Regions

86.33% (442/512) of the data are from the midwest or the south.  The Northeast only has 49 observations and the West has only 21. 


```{r}
sort(table(qualtrics$Region),decreasing = TRUE)
```

# Data viz by region 
```{r}
ggplot(aes(x = Region, y = well_score), data = qualtrics) + geom_boxplot() + theme_bw()
```

```{r}
ggplot(aes(x = Region, y = bmi), data = qualtrics) + geom_boxplot() + theme_bw()
```

## Proportion obese by region
```{r}
ggplot(aes(fill = Region, x = bmi), data = qualtrics) + geom_histogram() + theme_bw() + facet_wrap(~Region) + geom_vline(xintercept = 30, color = rgb(0,0,0,0.5))
```


## BMI and obesity by region

```{r}
qualtrics %>% group_by(Region) %>% summarize(mean_bmi = mean(bmi, na.rm = TRUE), 
                                             sd_bmi = sd(bmi, na.rm = TRUE), 
                                             prop_gt_30 = mean(bmi > 30, na.rm = TRUE), 
                                             n_bmi = sum(!is.na(bmi)), 
                                             n = n())
```


```{r}
qualtrics %>% group_by(Region) %>% summarize(
  mean_wellscore = mean(well_score, na.rm = TRUE),
  prop_gooddiet = mean(flag_gooddiet, na.rm = TRUE), 
  prop_depress = mean(flag_depress, na.rm = TRUE), 
  prop_htn = mean(flag_htn, na.rm = TRUE), 
  prop_cancer = mean(flag_cancer, na.rm = TRUE), 
  prop_hld = mean(flag_hld, na.rm = TRUE), 
                                             n = n())

```

# Hypothesis test
## Null: No difference between regions vs Alternative: Some means are different across regions 

# Good diet 

```{r}
prop.table(table(qualtrics$Region, qualtrics$flag_gooddiet),1)
chisq.test(table(qualtrics$Region, qualtrics$flag_gooddiet))
```
## Hyptertension 

```{r}
prop.table(table(qualtrics$Region, qualtrics$flag_htn),1)
chisq.test(table(qualtrics$Region, qualtrics$flag_htn), simulate.p.value = TRUE)
```
#Cancer

```{r}
prop.table(table(qualtrics$Region, qualtrics$flag_cancer),1)
chisq.test(table(qualtrics$Region, qualtrics$flag_cancer), simulate.p.value = TRUE)
```

## HLD
```{r}
prop.table(table(qualtrics$Region, qualtrics$flag_hld),1)
chisq.test(table(qualtrics$Region, qualtrics$flag_hld), simulate.p.value = TRUE)
```


## Flag Depress
```{r}
prop.table(table(qualtrics$Region, qualtrics$flag_depress),1)
chisq.test(table(qualtrics$Region, qualtrics$flag_depress), simulate.p.value = TRUE)
```
# Obesity
 We see significant differences across regions in regards to BMI.  Note: This won't be significant with any type of multipel hypothesis testing adjustment.  
```{r}
prop.table(table(qualtrics$Region, qualtrics$bmi > 30),1)
chisq.test(table(qualtrics$Region, qualtrics$bmi > 30), simulate.p.value = TRUE)
```

Note: Could we look at midwest vs other?  

# Continuous outcomes 
## Well diet score 
```{r}
mod <- lm(well_score ~ Region, data = qualtrics)
summary(mod)

#Checking assumptions
plot(mod)
```

#Log BMI
We see significant differences in BMI across the regions at the 0.05 level.  However, this won't be significant with any type of multiple hypothesis testing adjustment.  
```{r}
mod <- lm(log(bmi) ~ Region, data = qualtrics)
summary(mod)

#Checking assumptions
plot(mod)
```



1. Region differences (as defined by the US census) (https://www2.census.gov/geo/pdfs/maps-data/maps/reference/us_regdiv.pdf)
2. Then repeat but for Chicago. 







#Variables of interest
#Well diet score: well_score
#flag_gooddiet (1 for welldiet_score \> 60, 0 otherwise)
#flag_htn, 
#cancer
#hld
#bmi is there (>30 obese)
#flag_depress
#discrim_life_1 : discrim_life_5
#brs score = resiliency
#foodins_scores
#pss_score = perceived stress score
#aces_score
#commstress_score = community stress score



#Latitude and longitude

#bis is black idenity scale



